Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-22 paper/ijcai/paper.tex
another pass on initial section; finally going to eval

Intuitively, \ds{} identifies irrelevant parts of the code (\ie{},
parts that do not contribute to the fault) whereas \sfl{} ranks the
relevant parts of the code. It is conceivable, therefore, to combine
these two techniques based on the intuition that highly ranked
statements (as per \sfl{}), albeit covered by failing executions,
could be in fact unrelated to the fault (as per \ds{}). In fact, prior
work reported promising preliminary results on this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
Unfortunately, they used a small set of subjects in their evaluation
or archaic---often optimistic---methods to evaluate fault localization
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the issues from prior work. The study we conducted involves
\numFaults{} faults from \numPrograms{}
different programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. The contributions of this work
are: 1)~an empirical study, using real-world applications and bugs, on
the combination of \ds{} and \sfl{} for bug localization of
\emph{Java} faulty programs and 2)~a tool that implements the
combination of \ds{} with \sfl{}, coined \comb{}.  The tool as well as
a replication package will be available once double-blind requirements
are lifted.

@@

The first question \Fix{...elaborate...}
The second question addresses the problem that affects all dynamic
slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that of
missing faulty statements (see
Section~\ref{sec:slicing}). Understanding that issue is important; the
consequence for debugging is that developers would never be able to
locate faults. The third research question evaluates the impact of the
combination. To sum, our results show that the combination of the two
approaches improves the accuracy of fault localization on average by
\avgImprov\ in 51\% of the studied faults.

@@

>>>>

Intuitively, \ds{} identifies irrelevant parts of the code (\ie{},
parts that do not contribute to the fault) whereas \sfl{} ranks the
relevant parts of the code. It is conceivable, therefore, to combine
these two techniques based on the intuition that highly ranked
statements (as per \sfl{}), albeit covered by failing executions,
could be in fact unrelated to the fault (as per \ds{}). In fact, prior
work reported promising preliminary results on this
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair}.
Unfortunately, they used a small set of subjects in their evaluation
or over optimistic methods to evaluate fault localization
improvement~\cite{Wu:2014:CLC:2610384.2610386,Lucia:2014:FFL:2642937.2642983,Wen:2016:LLB:2970276.2970359}.

Given the importance of fault localization, this paper revisits the
problem of assessing the effectiveness of combining \ds{} and \sfl{},
addressing the key issues of prior work. We conducted a comprehensive
study involving \numFaults{} faults from \numPrograms{} different
programs from the Defects4J (D4J)
dataset~\cite{just-defects4j-issta2014}, which is frequently used to
evaluate fault localization research. Results show that \ds{} misses
faulty statements in 9\%\comments{(23 misses)} of the \numFaults{}
faults analyzed. Furthermore, we found that the combination of the two
approaches improves fault localization in 51\% of the cases with an
average improvement of \avgImprov. To sum, results indicate that the
risk of applying the technique is relatively low for the positive
impact it may bring and the tool implementing the technique works
out-of-the-box, \ie{}, it puts no requirements on the running
environment, subject programs it can be used, and requires no special
setup.

The contributions of this work are: 1)~an empirical study, using
real-world applications and bugs, on the combination of \ds{} and
\sfl{} for bug localization of \emph{Java} faulty programs and 2)~a
tool, dubbed \comb{}, implementing the \ds{}-\sfl{} combination. The
tool as well as a replication package will be available once
double-blind requirements are lifted.

@@

The first question evaluates the ability of dynamic slicing reducing
application code. Improvements on fault localization depends on that
ability. The second question addresses the problem that affects all
dynamic slicing techniques~\cite{Lin:2018:BDE:3238147.3238163}---that
of missing faulty statements (see
Section~\ref{sec:slicing}). Developers would not be able to
successfully debug code if that issue is manifested. The third
research question evaluates the impact of the combination as
substantiated by \comb.

@@

\Fix{
The main lesson of this work is that
fault localization research should consider compare new techniques
against this combination.}
